The paper on blockchain front-running

### 2018-09-20 frontrunning/Latex/sections/abstract.tex
Some edits

% !TEX root = ../main.tex
\begin{abstract}

Abstract goes here.

>>>>

% !TEX root = ../main.tex

\begin{abstract}

We consider \textit{front-running} to be a course of action where an entity benefits from prior access to privileged market information about upcoming transactions and trades. Front-running has been an issue in traditional financial instrument markets since the 1970's. With the advent of the blockchain technology, front-running resurfaced in new forms we explore here, due blockchain's decentralized and transparent nature.
In this paper, we consider instances of front-running across the top 25 decentral applications (DApps) deployed on Ethereum. Additionally, we carry out detailed analysis of \textsf{Status.im} initial coin offering (ICO) and show evidence of abnormal miner's behaviour indicative of front-running token purchases.  
Finally, we introduce a framework for categorizing proposed solutions to front-running and examine the applicability to the identified issues.

### 2018-09-20 frontrunning/Latex/sections/paper.tex
Some edits

The concept of the \emph{front-running} is decades old starting with early financial markets. Initially, the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, could run in front of the others to get their orders ahead of the change in the market to profit from the price change. Clearly, in such scenarios front-running was possible yet not detectable as a damaging activity. However, with the rapid advances of the technology in the last few decades, trading is not carried out in person anymore, a new form of front-running is feasible through high-speed networks. Furthermore, Blockchain technology has introduced transparency and open markets and leads to a new era of front-running which inherently affects all decentral applications, whether financial or non-financial. Arbitrage and Censorship, are also issues that have been linked to front-running attacks on blockchain \textit{(We need to talk about why these two are left out of the scope of this paper)}. Currently, there are quite a few decentral applications built on the blockchains, so in order for us to perform a thorough study on blockchain application front-running, we set a specific criteria by using the top 25 decentral applications which have the highest recent user activities.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} Using this criteria, we successfully categorized these decentral applications into 4 principal categories on which we conduct our analysis. Surprisingly, there was no ICO (initial coin offering) included in the top 25 DApps list by the time we fetched the data from the website. We believe the reason is that the ICOs are inherently different from other groups of Daaps as they are merely highly active during their offering periods and their user activity drops dramatically after the offerings period are over. Therefore, we  consider ICOs as other cases on which the front-running should be investigated (although they are not listed in the top 25 DApps we use) \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}

@@

There have been more than 3000 ICOs on Ethereum alone, estimated to exceed 75 billion dollars in the first half of 2018~\cite{zetzsche2018ico}. On our DApp samples, there was not ICOs mainly because they tend to run for a short time with a high number of participant and in the time of writing no ICOs have reached the top 25 DApps of \texttt{DAppRadar.com}. Needless to say, the importance of ICOs as an application of blockchain requires more in-depth analysis of front-running on these type of DApps. %ICOs due to the defined cap is similar to our analogy of a queue line, people would line up to get in and there's an opportunity to front-run. 
Here we focus on one ICO that our preliminary research showed that there might have been a front-running incident. There is no doubt that similar behaviour could be seen in other instances of ICOs or similar DApps if investigated.

\subsection{\textit{Status.im} ICO}
As discussed in~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, \textit{Status.im} ICO is such an application. In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the predefined cap within 3 hours, resulting in close to 300,000 Ether of funds. In order to prevent few large investments to buy up all the tokens and limit the amount of Ether deposited in an investment, they used a \textit{fair} token distribution method named \textit{Dynamic Ceiling} as an attempt to increase the opprotunity window for smaller investors. They implemented multiple caps --ceiling-- in which, each had a maximum amount that could be deposited in. In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to their multi-signature wallet address~\cite{statusicoanalysis}.

>>>>

The concept of  \emph{front-running} is decades old starting with early financial markets. Initially, the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, could run in front of the others to get their orders ahead of the change in the market to profit from the price change. Clearly, in such scenarios front-running was possible yet not detectable as a damaging activity. However, with the rapid advances of the technology in the last few decades, trading is not carried out in person anymore, a new form of front-running is feasible through high-speed networks. Furthermore, Blockchain technology has introduced transparency and open markets and leads to a new era of front-running which inherently affects all decentral applications, whether financial or non-financial. Arbitrage and Censorship, are also issues that have been linked to front-running attacks on blockchain \textit{(We need to talk about why these two are left out of the scope of this paper)}. Currently, there are quite a few decentral applications built on the blockchains, so in order for us to perform a thorough study on blockchain application front-running, we set a specific criteria by using the top 25 decentral applications which have the highest recent user activities.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} Using this criteria, we successfully categorized these decentral applications into 4 principal categories on which we conduct our analysis. Surprisingly, there was no ICO (initial coin offering) included in the top 25 DApps list by the time we fetched the data from the website. We believe the reason is that the ICOs are inherently different from other groups of Daaps as they are merely highly active during their offering periods and their user activity drops dramatically after the offerings period are over. Therefore, we  consider ICOs as other cases on which the front-running should be investigated (although they are not listed in the top 25 DApps we use) \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}

@@

There have been more than 3000 ICOs on Ethereum alone, estimated to exceed 75 billion dollars in the first half of 2018~\cite{zetzsche2018ico}. In Table~\ref{top25DApps}, no ICO is represented in the top 25. This is because they tend to be high in activity for a short duration only---namely during their sale. Since no major ICO was active on the day that we sampled \texttt{DAppRadar.com}, the ICO category falls through our sampling method. However we identify this as a major category and study it here.

%. Needless to say, the importance of ICOs as an application of blockchain requires more in-depth analysis of front-running on these type of DApps.

%ICOs due to the defined cap is similar to our analogy of a queue line, people would line up to get in and there's an opportunity to front-run.

%Here we focus on one ICO that our preliminary research showed that there might have been a front-running incident. There is no doubt that similar behaviour could be seen in other instances of ICOs or similar DApps if investigated.

\subsection{\textit{Status.im} ICO}
As discussed in Section~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, \textit{Status.im} ICO is such an application. In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the predefined cap within 3 hours, resulting in close to 300,000 Ether of funds. In order to prevent few large investments to buy up all the tokens and limit the amount of Ether deposited in an investment, they used a \textit{fair} token distribution method named \textit{Dynamic Ceiling} as an attempt to increase the opprotunity window for smaller investors. They implemented multiple caps --ceiling-- in which, each had a maximum amount that could be deposited in. In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to their multi-signature wallet address~\cite{statusicoanalysis}.
